Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-04-14 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating results section with descriptions, captions for new figures

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim20$ events, meaning a single run does not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied.

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: https://github.com/rice-solar-physics/IonPopSolver} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).

@@

	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. Furthermore, for each of the $N_R$ runs per $t_N$ value, we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

@@

		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (blue). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

@@

	\hl{Move this to results eventually.} All of the data analysis shown in this work was carried out using the IPython system for interactive scientific computing in Python as well as the NumPy and Scipy numerical and scientific Python libraries \citep{perez_ipython:_2007,van_der_walt_numpy_2011}. All plots were produced using the Matplotlib graphics environment \citep{hunter_matplotlib:_2007}.

>>>>

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. \hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied. Thus, when $t_N=5000$ s and $N\sim15$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

	\par In order to compactly summarize all of the data in each run of our model, we calculate the resulting emission measure distribution using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at time $t_i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. Furthermore, each emission measure distribution we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$, using $T_{eff}$, the effective temperature calculated by including effects due to NEI.

@@

	\par As noted in \autoref{subsec:heating_stats}, for each heating frequency $t_N$, we compute $N_R$ runs such that there are $N_R$ $\mathrm{EM}(T)$ distributions for each $t_N$. Thus, the $\mathrm{EM}(T)$ that we show for each $t_N$ is the average computed over all $N_R$ of these emission measure distributions. 

@@

		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par First, we look at the resulting emission measure distributions for the case in which only the electrons are heated. \autoref{fig:el_em} shows $\mathrm{EM}(T)$ for six different values of $t_N$ and three different types of heating functions: uniform heating events, events chosen from a power-law distribution of index $\alpha=-2.5$, and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event. The dotted lines in each frame show the corresponding emission measure distribution constructed from $T_{eff}$, $\mathrm{EM}(T_{eff})$.
	\par As $t_N$ increases, $\mathrm{EM}$ is allowed to extend to both lower and 

@@

	\hl{Acknowledge some things here.} 
